---
title: "Score Report"
format: docx
toc: true
params:
  program_name: NA
  data_file_path:
  
  # If adding more or different parameters (e.g., Year, Semester) will need to add to or change the params list.
---

```{r setup, include=FALSE}
#| warning: FALSE
#| message: FALSE

knitr::opts_chunk$set(error=FALSE)

options(digits = 3) # Setting the number of digits for the entire document

required_packages <- c("tidyverse", "ggplot2", "htmlTable", "openxlsx", "flextable", "psych", "stringr")

# Call packages
for (pkg in required_packages) {
    library(pkg, character.only = TRUE)
}
```

```{r Identifying Program, include=FALSE}
program <- params$program_name
```

```{r DateBlock, message=FALSE}
#| echo: FALSE
#| eval: TRUE

Analysis <- print(paste("This analysis was conducted on", program, "data"))

current_date <- format(Sys.Date(), "%B %d, %Y")

#Date <- print(paste0("This Report was generated on ", current_date))

```

This report was generated on `{r} current_date` for `{r} program`.  

# *Description of Measure*
The Force Concept Inventory (FCI) is a standardized physics assessment used by universities to evaluate and compare students' conceptual understanding of Newtonian mechanics. Administered as a 12-question multiple-choice quiz, the FCI is commonly given to STEM majors at different points in their academic journey—such as at the beginning and end of introductory physics courses—to track student progression and measure learning gains. Institutions use FCI results to assess instructional effectiveness, identify persistent misconceptions, and compare cohorts over time, helping to inform curriculum improvements and teaching strategies in physics education.

# *Results*

## *Average Score*

```{r Total}
#| echo: FALSE

#Read in the data

data <- read.xlsx("./Data/Data_Large.xlsx")

#Filter by program
filtered_data <- data |>
  filter(Program == program)

#Make a total score
filtered_data$total <- rowSums(filtered_data[5:16])

```

The average score for all `{r} program` students was `{r} mean(filtered_data$total)`.  

```{r Cleaning up Global Environment, include=FALSE}
rm(list = ls()[sapply(mget(ls()), is.data.frame)])
rm(ft, p, new_columns)
```
