---
title: "Program_Gen_File"
format: docx
toc: true
params:
  program_name: NA
  Year: NA
  Sem: NA
  # If adding more or different parameters (e.g., Year, Semester) will need to add to or change the params list.
---

```{r setup, include=FALSE}
#| warning: FALSE
#| message: FALSE

knitr::opts_chunk$set(error=FALSE)

options(digits = 3) # Setting the number of digits for the entire document

required_packages <- c("tidyverse", "ggplot2", "htmlTable", "openxlsx", "flextable", "psych", "stringr")

# Call packages
for (pkg in required_packages) {
    library(pkg, character.only = TRUE)
}

# Setting parameters for flextable

set_flextable_defaults(
  font.size = 12, theme_fun = theme_vanilla,
  padding = 6,
  background.color = "#FFFFFF")
```

```{r Specifying Params}
#| echo: FALSE

program <- params$program_name
Years <- params$Year
Sem <- params$Sem

```

```{r DateBlock, message=FALSE}
#| echo: FALSE
#| eval: TRUE

Analysis <- print(paste("This analysis was conducted on", program, "data"))

current_date <- format(Sys.Date(), "%B %d, %Y")

#Date <- print(paste0("This Report was generated on ", current_date))

```

This report was generated on `{r} current_date` for `{r} program`. 

# *Description of Measure*
The Force Concept Inventory (FCI) is a standardized physics assessment used by universities to evaluate and compare students' conceptual understanding of Newtonian mechanics. Administered as a 12-question multiple-choice quiz, the FCI is commonly given to STEM majors at different points in their academic journey—such as at the beginning and end of introductory physics courses—to track student progression and measure learning gains. Institutions use FCI results to assess instructional effectiveness, identify persistent misconceptions, and compare cohorts over time, helping to inform curriculum improvements and teaching strategies in physics education.

# *Results*

## *Average Score*
```{r Average Score Table}
#| echo: FALSE

# Reading in data
data <- read.xlsx("./Data/Data_Large.xlsx")

# Filtering by program
filtered_df <- data %>% 
  filter(Program == program, Year == Years, Semester == Sem)

# Creating Total score

filtered_df$Tot <- rowSums(filtered_df[5:16])

aggregated_df <- filtered_df %>%
  group_by(Year) %>%
  summarise(Average_Score = mean(Tot, na.rm = TRUE))

flextable(aggregated_df)
```

## *Figure 1*

```{r Average Score Graph}
#| echo: FALSE
#| warning: FALSE
ggplot(filtered_df, aes(x = Tot, fill = Year)) +
  geom_histogram(aes(y = ..density..), alpha = 0.5, bins = 30, position = "identity") +
  geom_density(aes(color = Year, fill = Year), alpha = 0.5, linewidth = 1) +
  scale_fill_manual(values = c("First" = "#450084", "Second" = "#CBB677")) +
  scale_color_manual(values = c("First" = "#450084", "Second" = "#CBB677")) +
  theme_minimal() +
  labs(title = "Distribution of Total Scores", x = "Total Scores", y = "Density")
```

```{r Cleaning up Global Environment, include=FALSE}
rm(list = ls()[sapply(mget(ls()), is.data.frame)])
rm(ft, p, new_columns)
```
