---
title: "Complex Parent File"
format: pdf
---

# Parent File

This file contains all of the libraries, folder/file paths, and further specifications of assessments.

## Libraries

Add or remove libraries as desired

```{r Libraries}
required_packages <- c("tidyverse", "ggplot2", "htmlTable", "openxlsx", "flextable", "psych", "stringr")

# Check and install packages if needed
for (pkg in required_packages) {
  if (!requireNamespace(pkg, quietly = TRUE)) {
    install.packages(pkg)
    library(pkg, character.only = TRUE)
  } else {
    library(pkg, character.only = TRUE)
  }
}
```

## Folders and File Path

Create and/or Specify the folder in which you will be working in and where you would like your reports to output to

### Folders

```{r Folders}
# Create a folder structure for storing reports
# The first line creates a "parent folder" named "Reports" in the current working directory.
# The second line creates a "subfolder" named "Tables" within the "Reports" folder.

dir.create("./Reports") # Creates the "Reports" folder in the current working directory
dir.create("./Reports/Excel Workbooks") # Creates the "Tables" subfolder within the "Reports" folder

# The "Tables" subfolder is useful if saving out Excel sheets for each assessment. This is helpful when dealing with a large number of assessments as well as a large number of automated reports.

dir.create("./Data") # Creates a folder to house data files to maintain a consistent folder structure for year-to-year or semester-to-semester reporting
dir.create("./Children") # Creates a folder to house the child/children files we will create
```

### File Paths

Specifying File Paths

```{r File Paths}

# Define file paths for a project folder structure

# The base path is set to the current working directory using "./".
# All subsequent file paths are constructed relative to this base path.

path <- "./"  # Base path representing the current working directory

# File paths for specific subdirectories:
Children_file_path <- paste0(path, "Children/") # Path for the "Children" folder
data_file_path <- paste0(path, "Data/")         # Path for the "Data" folder
report_file_path <- paste0(path, "Reports/")    # Path for the "Reports" folder


# Specify the data file name below
# Housing in the parent file enables for higher flexibility of the Child file
data_file_name <- "Data_Large"

```

### Further Specifications

Obtaining Factors (Variables) and levels in Data

```{r File Paths}
probe <- read.xlsx(paste0(data_file_path, "Data.xlsx"))

# This is a simple simulated data set that is likely not reflective of real data; however, you can may already know how you want to segment your data for reporting.

# Select only the columns with character data - Since our classifying characteristics (e.g., Year, Semester, Program) are the only character values this is a quick and easy way to isolate out values.
probe <- probe[, sapply(probe, is.character)]

unique_values <- lapply(probe, unique)

```

# Running Child File

```{r Child}

#Program Specific
Program_list <- unique_values$Program # Pulling from out unique_values list
Year_list <- unique_values$Year # Pulling from out unique_values list
Semesters_list <- unique_values$Semester # Pulling from out unique_values list

# Staged loop: Looping through Years, Semesters, and Programs
for (i in 1:length(Year_list)) {
  for (j in 1:length(Semesters_list)) {
    for (k in 1:length(Program_list)) {
      Year <- Year_list[i]
      Sem <- Semesters_list[j]
      program_name <- Program_list[k]
        # Use the Value names specified in the latest for loop
        # This will vary the name of the file output for each group analyzed
      output_file_name <- paste0(program_name, "_", Year, "_", Sem, "_Report.docx")
      output_path <- file.path(report_file_path, output_file_name)
    
      quarto::quarto_render(
        # The name of the Child file you are using
        input = "Child_501.qmd",
        # The naming convention of the output file defined above
        output_file = output_file_name,
        # params are the list of parameters ported over from the Parent file into the Child file.
        # You must update the YAML header under "params" to reflect the variables you are porting over.
        execute_params = list(program_name = program_name, Year = Year, Sem = Sem)
      )
      
      #Move the file to the correct location
      file.rename(output_file_name, output_path)
    }
  }
}
```
